Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
italics in correctly classified

Table~\ref{resultsTable} shows the results of running the two data sets through the
default Weka J48 decision tree algorithm.  Without downsampling, the 
decision tree shows an increase of 4.09\% correctly classified instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
had a classification accuracy of 64.10\%, which outperformed the baseline of
guessing all builds passed (50.00\%).
 After including the social data
in the data set, the classifier correctly predicted 76.09\% of the data set,
about a 12\% improvement from only the technical data.  These results show that
both technical and social data can be used to improve predictions of build 
integration success.

It is also worth noticing that in both cases the Kappa statistic increases when
adding social data (100\% and 85\% respectively) which represents a more robust
measure than Correctly classified instances\todo{Whenever you use a phrase that
  is a key label in your data (like ``Correctly classified''), find a way to
  typeset it differently so it scans as an important concept.  Quotes or Italics/emphasis
  is fine.}, since it takes into account the
correctly guessed instances occurring by chance, and we may also notice that the
Mean absolute error decreases, giving stronger confidence to our claims when
considering eventual outcomes.

>>>>

Table~\ref{resultsTable} shows the results of running the two data sets through the
default Weka J48 decision tree algorithm.  Without downsampling, the 
decision tree shows an increase of 4.09\% \textit{correctly classified} instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
had a classification accuracy of 64.10\%, which outperformed the baseline of
guessing all builds passed (50.00\%).
 After including the social data
in the data set, the classifier correctly predicted 76.09\% of the data set,
about a 12\% improvement from only the technical data.  These results show that
both technical and social data can be used to improve predictions of build 
integration success.

It is also worth noticing that in both cases the Kappa statistic increases when
adding social data (100\% and 85\% respectively) which represents a more robust
measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance, and we may also notice that the
Mean absolute error decreases, giving stronger confidence to our claims when
considering eventual outcomes.
